### 2014-01-24 thesis/src/chapters/chapter-state-of-the-art.tex
Thesis: add key technical concepts section of CF evaluation

\subsubsection{Scalability}
\emph{Cloud foundry} supports only horizontal scaling.

>>>>

\subsubsection{Scalability}
\emph{Cloud foundry} supports only horizontal scaling not only within one provider, but also across many. This feature is called \emph{Multi-Cloud} in Cloud Foundry nomenclature.

\subsubsection{Cloud-federation awareness}
As it was stated in previous sections, Cloud Foundry is \emph{cloud-federation aware}, i.e. it allows users to span their applications across many providers, which results in a hybrid solution that comes in many flavours: \emph{public-public}, \emph{public-private} or \emph{private-private}.

% do kminy - dopisac Bosha/DEA/Warden ?
